```{r}
require(gplots)
require(igraph)

```

```{r}
library(sna)
library(statnet)
library(network)
```
#Evaluate either the structural or regular equivalency of the lawyers using the advice network (your choice -- either is justifiable). Plot the resulting dendrogram and decide how many equivalency classes to define (i.e., how many groups $k$), providing a brief discussion of your decision process for selecting that number of classes. [2 points]

```{r}
el_ad <- read.csv("Law_Advice.csv", header = TRUE, as.is = TRUE)
law_att <- read.csv("Law_NodeAtt.csv", header = TRUE, as.is = TRUE)
advice <- graph_from_edgelist(as.matrix(el_ad), directed = TRUE)

## for ease of plotting, also making a network that is the union of all three networks


attify <- function(n_net){
  V(n_net)$names <- V(n_net)
  V(n_net)$Status <- law_att$Status
  V(n_net)$Gender <- law_att$Gender
  V(n_net)$Office <- law_att$Office
  V(n_net)$Seniority <- law_att$Seniority
  V(n_net)$Age <- law_att$Age
  V(n_net)$Practice <- law_att$Practice
  V(n_net)$LawSchool <- law_att$LawSchool
  return(n_net)
}
advice <- attify(advice)



net_ad <- get.edgelist(advice)
net_ad <-network(net_ad)
net_ad
```


```{r}
ad_ec <- equiv.clust(net_ad, 
                     mode="graph",
                     plabels = network.vertex.names(net_ad))

plot(ad_ec,
     labels = network.vertex.names(net_ad))
rect.hclust(ad_ec$cluster, k = 3) 
```



```{r}
ad_bm <- blockmodel(net_ad, ad_ec, k = 3) ## simplifying the network into a blockmodel based on these measures of structural equivalence
ad_bm

```

```{r}
gplot(net_ad,
      vertex.col = ad_bm$block.membership[order(ad_bm$order.vector)],
      label = network.vertex.names(net_ad),
      displaylabels = TRUE)

```
For question one I decided to find structural equivalence as I want to know which lawyers hold the same position and role in terms of advice-giving within the law firm. structural equivalence means that two structures have the same abstract form or shape, and their elements can be related in such a way that all the properties and relationships between elements in one structure are preserved in the other structure. 

I decided to have 3 clusters as the organization has three offices Boston, Hartford, Providence. Thus, I wanted how dissimilar are the position and role that lawyers possess in regards to advice-giving within different offices. 

The height in a cluster dendrogram represents the distance or dissimilarity between the clusters being joined at each step of the hierarchical clustering process. The vertical axis of the dendrogram is typically labeled with a distance metric, such as Euclidean distance or correlation coefficient, which is used to measure the dissimilarity between clusters. The higher the point of joining in the dendrogram, the greater the dissimilarity or distance between the clusters. Therefore, high points on the dendrogram indicate greater differences or distances between the clusters. As we see lawyers with ID of 71, 67, 58, and 59 have the same height therefor they hold similar positions within the cluster.As we see these lawyers share the same status within the law organization; thus, we can conclude that lawyers with similar status have similar structural equivalence.  

ID	Status	Gender	Office	Seniority	Age	Practice	LawSchool
67	2	2	1	1	35	1	2
71	2	2	1	1	26	1	2
59	2	2	2	2	30	1	2
58	2	1	2	3	33	1	3



#Compare the various groupings that we have (status, gender, office, practice) with the equivalency classes you define. Identify the vertex attribute that appears to be most closely aligned with the resulting equivalency classes. [1 point]

```{r}
ad_memb<-ad_bm$block.membership
compare(ad_memb, V(advice)$Office, method = "nmi")
compare(ad_memb, V(advice)$LawSchool, method = "nmi")
compare(ad_memb, V(advice)$Seniority, method = "nmi")
compare(ad_memb, V(advice)$Status, method = "nmi")
compare(ad_memb, V(advice)$Gender, method = "nmi")
compare(ad_memb, V(advice)$Practice, method = "nmi")
```
"If the two memberships are identical, they will have a value of 1, while those close to 0 are uninformative of one another". The result shows that lawyers with the same status (0.6804327) are most closely aligned with the resulting equivalency classes. However, lawyers with the same practice (0.004619328) attribute has the least alignment with the resulting equivalency classes.
Status: (1 = partner (a more senior position); 2=associate (a more junior position))
Practice: (1 = litigation; 2 = corporate)

#Plot the advice network twice - once with nodes coloured by their equivalency class membership and once with nodes coloured by the vertex attribute that you have identified. Make sure that the layout stays consisten t between the two plots to facilitate comparison. [2 points]
```{r}
gplot(net_ad,
      vertex.col = ad_bm$block.membership[order(ad_bm$order.vector)],
      label = network.vertex.names(net_ad),
      displaylabels = TRUE)

```



```{r}
plot(advice,
     vertex.color = V(advice)$Office,
     vertex.label =  V(advice)$ID,
     vertex.size = ad_bm$block.membership[order(ad_bm$order.vector)]*5,
     edge.arrow.size = 0.15,
     edge.width = 0.3,
     edge.curved = 0.3,
     main = "Advice")

legend("topright",
       legend = c("Boston", "Hartford", "Providence"),
       pch = 19,
       col = categorical_pal(8)[c(1:3)])
    
```

```{r}
plot(advice,
     vertex.color = V(advice)$Status,
     vertex.label =  V(advice)$ID,
     vertex.size = ad_bm$block.membership[order(ad_bm$order.vector)]*5,
     edge.arrow.size = 0.15,
     edge.width = 0.3,
     edge.curved = 0.3,
     main = "Advice")

legend("topright",
       legend = c("Partner", "Associate"),
       pch = 19,
       col = categorical_pal(8)[c(1:2)])

```




#Discuss what these results imply about the nature of advice-giving among the lawyers and the roles that the lawyers occupy in the firm. You may want to draw in additional information to explore/illustrate. [5 points]

"Structural affinity reflects the extent to which actors are similar to each other in
terms of their relations with other actors, or in terms of the similarity of their traits, in relation to other actors’ traits"(Galaskiewicz & Burt, 1991). Class membership in a one-mode network structural equivalence refers to the assignment of nodes to different classes or categories based on their similarity in terms of their patterns of ties. Nodes in the same class are considered more similar to each other than to nodes in other classes. The results imply that the nature of advice-giving among lawyers is typically based on their legal expertise and status, rather than their age, gender, office, or law school. Lawyers in a firm may hold different roles such as partners and associates in the case of Lazega lawyers network.Typically having more senior position and decision-making authority gives a lawyer the advantage of being able to give-advice to junior lawyers. Lawyers with similar Status and seniority are often holding the same structural equivalence and are allocated within the same cluster.


As the second graph shows lawyers within the same office are categorized in different clusters within a network which indicates lawyers within the same office are not holding the same position/role. However, the third graph states that lawyers with similar status (associate or partner) are more similar as they are allocated within the same order. Basically associate lawyers are allocated in cluster 3 and partners are allocated in cluster 1 and 2. We can conclude that associate lawyers who have more senior position are sharing more similarities in terms of giving advice while partner lawyers are more similar in terms of receiving advice.











Sign in. RPubs. (n.d.). Retrieved February 13, 2023, from https://rpubs.com/pjmurphy/325575 

Galaskiewicz, J., & Burt, R. S. (1991). Interorganization Contagion in Corporate Philanthropy. Administrative Science Quarterly, 36(1), 88–105. https://doi.org/10.2307/2393431